Supplementary material

### 2022-02-03 analysis/supplementary-materials/supplementary.Rmd
Adding previous shoreline dates

>>>>

```{r brunstad24, echo = FALSE, out.width = "500px", regfloat=TRUE}
knitr::include_graphics(here("analysis/figures/brunstad24.png"))

filter(rcarbon, site_name  == "Brunstad 24") %>% 
  select(lab_code, c14_bp, error, material, context) %>% 
   kable(caption = "Brunstad 24", col.names = c("ID",
                    "\\textsuperscript{14}C BP",
                    "Error",
                    "Material",
                    "Context"),
        booktabs = TRUE,  linesep = c(""), escape = FALSE)
```

```{r brunstad25, echo = FALSE, out.width = "500px", regfloat=TRUE}
knitr::include_graphics(here("analysis/figures/brunstad25.png"))

filter(rcarbon, site_name  == "Brunstad 25") %>% 
  select(lab_code, c14_bp, error, material, context) %>% 
   kable(caption = "Brunstad 25", col.names = c("ID",
                    "\\textsuperscript{14}C BP",
                    "Error",
                    "Material",
                    "Context"),
        booktabs = TRUE,  linesep = c(""), escape = FALSE)
```
